Binarity's Biases on Transit Survey Occurrence Rates

### 2018-02-19 paper/main.tex
update shortauth
match AAS submission standards

\shortauthors{Bouma et al.}
\shorttitle{Binarity's Biases}

@@

\title{ The effects of binarity on planet occurrence rates measured by
transit surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%

@@

The astronomers analyze their data assuming that all stars are
single.  In particular they do not have accurate enough parallaxes to
tell that some of the stars are apparently overluminous.  They want to
compute the number of planets with size $r$ per star of mass $M$.  If
the total number of stars for which such planets could be detected
($N_\star$) and the number of detected planets ($N_{\rm det}$) are
both large, then the astronomers' estimate for the occurrence rate
($\Lambda$) is simply
\begin{equation}
  \Lambda = \frac{N_{\rm det}}{N_\star}
                    \cdot \frac{1}{p_{\rm tra}},
\label{eq:occ_rate_simple}
\end{equation}
where the geometric transit probability, $p_{\rm tra}$, accounts for
the fact that most planetary orbits are not aligned close enough with
our line of sight to produce transits.

@@

To calculate the occurrence rate of each planet type, our observers
identify the ``stars'' from their survey that appear to have been
searched for signals of each depth.  These transits are detected
within a certain maximum
distance~\citep[see][]{pepper_using_2003,pepper_searching_2005}, which
from Equation~\ref{eq:S_N_thresh} scales as
\begin{equation}
  d_{\rm max} \propto \delta \cdot L_{\rm tot}^{1/2}.
  \label{eq:dmax}
\end{equation}
Assuming that stars are uniformly distributed in space, the number of
searchable stars $N_\star$ is proportional to
\begin{equation}
    N_\star \propto n \delta^3 L_{\rm tot}^{3/2},
\label{eq:N_searchable_prop}
\end{equation}
where $n$ is the number per unit volume of single or binary star
systems.

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Apparent occurrence rate $\Lambda\a$, and occurrence rate for
        singles $\Lambda_0$, for a model with one type of star, one
        type of planet, and twin binaries (same as
        Figure~\ref{fig:model_1_volumes}).  We assume a twin binary
        fraction of $0.05$, and that single, primary, and secondary
        stars host planets at equal rates.  If the true planet radius
        is $r\p$, all planets detected in binaries will have apparent
        radii $r\a = r\p/\sqrt{2}$; Equation~\ref{eq:ratios} gives the
        normalizations.
    }
    \label{fig:occ_rate_model_1}
\end{figure}

@@

Suppose the occurrence rate densities for planets around
single stars, primaries, and secondaries are $\Gamma_0(r),
\Gamma_1(r)$, and $\Gamma_2(r)$, respectively. For a single planet
size,
\begin{equation}
    \Gamma_i(r) = \Lambda(r\p) \cdot \hat{\delta}(r-r\p),~~{\rm for}
    \ i\in\{0,1,2\},
    \label{eq:one_planet}
\end{equation} 
where $\hat{\delta}$ is the Dirac delta function.
The number of planets detected from singles, primaries, and
secondaries are then
\begin{align}
  n_{\rm det}^0(r\a)\mathrm{d}r\a &= 
      \frac{N_\star(r\a)}{1+\mu} p_{\rm tra}
      \Gamma_0(r\a)\mathrm{d}r\a,
  \label{eq:n0} \\
  n_{\rm det}^1(r\a)\mathrm{d}r\a &= 
      \frac{\mu N_\star(r\a)}{1+\mu} p_{\rm tra}
      \Gamma_1(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n1} \\
  n_{\rm det}^2(r\a)\mathrm{d}r\a &=
      \frac{\mu N_\star(r\a)}{1+\mu} p_{\rm tra}
      \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n2}
\end{align}
where $n_{\rm det}^i$ is the number of detections per unit apparent
radius for each respective type of star.

@@

We want an equation for $\Gamma\a(r\a,M\a)$, the apparent rate density
at each apparent planet radius and apparent stellar mass\footnote{By
assumption, the apparent stellar mass for single star systems is the
true mass. For binary systems, the apparent mass is the mass of the
primary.}.
Similar to Equation~\ref{eq:rate_density_defn}, we define
$\Gamma(r,M)$ as the number of planets per star, per unit planet radius,
per unit stellar mass.  Due to the varying binary mass ratios, we need
the following modifications to Equation~\ref{eq:formula_twin_binary}:
%
\begin{enumerate}
%
\item The Malmquist bias is different. The ratio between the number of
binary and single systems for which a transit of depth $\delta$ is
detectable, $\mu$, has changed.  At any $(r\a,M\a)$ pair, the number
of binary systems in the searchable volume with mass ratio $(q,
q+\mathrm{d}q)$ is now
\begin{equation}
    {N_\star(r\a)\over{1+\mu}}\cdot {n_{\rm b}\over n_{\rm s}}
    \left[{L_{\rm tot}(M\a, q) \over L(M\a)}\right]^{3/2}
    f(q)\,\mathrm{d}q,
    \label{eq:N_binaries}
\end{equation}
where $\mu$ is given by
\begin{equation}
    \mu= 
    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L_{\rm tot}(M\a, q)
    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
Binaries with larger mass ratios are overrepresented by a factor of
$\left[{L_{\rm tot}(M\a, q)/L(M\a)}\right]^{3/2}$ because the
sample of searchable binaries is magnitude-limited.  To obtain
the number of binary systems searched at each $(r\a,M\a)$ pair,
Equation~\ref{eq:N_binaries} needs to be integrated over $q$.  It
can then replace ${\mu N_\star(r\a)/(1+\mu)}$ in
Equations~\ref{eq:n1} and~\ref{eq:n2}.

@@

Taking these modifications into account, a general formula for the
apparent rate density follows:
\begin{align}
    \notag
    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu} \cdot
    \left\{ \Gamma_0(r\a, M\a)+ 
    \frac{n\b}{n\s}
    \left[ \int_0^1 \mathrm{d}q \,
           \mathcal{D}_1^3 f(q)\cdot
           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a)\,
    \right.   
    \right. \\
    & \quad\quad\quad\quad\quad \left.\left.
    +\int_0^1 {\rm d}q\, 
         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
         \frac{R(qM\a)}{R(M\a)} q^{-1/3}
    \right] \right\}.
    \label{eq:general_Gamma_a}
\end{align}
We give an alternative derivation in the
\hyperref[sec:appendix]{Appendix}.
With the definition of $\mu$ in Equation~\ref{eq:mu_general},
Equation~\ref{eq:general_Gamma_a} can also be expressed as
\begin{align}
    \notag
    \notag
    \Gamma\a(r\a,M\a)
    &= 
    {1\over 1+\mu} \cdot
    \left[
       \Gamma_0(r\a, M\a)\phantom{\tilde \Gamma}\right.&\\
       &\left.+\mu\cdot
       \left\langle
       \mathcal{D}_1\cdot\Gamma_1\left(\mathcal{D}_1r\a, M\a\right)
       +
       {q \mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a,
       qM\a\right) \cdot {R(qM\a) \over R(M\a)}q^{-1/3}
       \right\rangle
    \right],
\end{align}
where the angle brackets denote averaging over $\mathcal{D}_1^3f(q)$.
Summarized, the apparent rate density is a weighted sum of the rate
densities from singles, primaries, and secondaries.  The weights are
determined by the fraction $\mu$ and mass ratio distribution
$\mathcal{D}_1^3f(q)$ of binaries {\it in the searchable volume}.  The
fraction $\mu$ gives the relative contributions from singles and
binaries, and $\mathcal{D}_1^3 f(q)$ applies a Malmquist bias for
binaries that are brighter.  A final correction for secondaries
accounts for the overestimated transit probability.

@@

The rate density now varies not only with planet radius, but also
host star mass.  We can absorb this dependence into a power law,
\begin{equation}
    \Gamma_i(r,M) = Z_i \cdot \frac{r^\gamma}{\mathcal{N}_r} \cdot
    \frac{M^\zeta}{\mathcal{N}_M},
\end{equation}
where $Z_i$ is dimensionless, and the normalization constants carry
the units.% (each side has units $[r^{-1} M^{-1}]$).

@@

\begin{figure}[!t]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
    \caption{
        {\it Left:} apparent rate density ($\Gamma\a$) and single star
        rate density ($\Gamma_0$). {\it Right:} apparent occurrence
        rate ($\Lambda\a$) and single star occurrence rate
        ($\Lambda_0$), over $0.5r_\oplus$ bins.  The true planet
        radius distribution is specified by
        Equation~\ref{eq:model3_radius_distribution}.  This model
        assumes that the observer knows the true properties of all the
        singles and primaries, and that the volume-limited mass ratios
        of secondaries are drawn from a uniform distribution. Further,
        we take $Z_0=Z_1=0.5$ throughout; $Z_0,Z_1,Z_2$ are the number
        of planets per single, primary, and secondary star.  The rate
        and rate density are related by $\Lambda|_a^b =
        \int_{a}^{b}\Gamma\,{\rm d}r$.
    }
    \label{fig:occ_rate_model_3_log}
\end{figure}

@@

\acknowledgements{
It was a pleasure discussing this study with T.~Barclay, W.~Bhatti,
J.~Christiansen, F.~Dai, and T.~Morton.  This work made use of NASA's
Astrophysics Data System Bibliographic Services.
%
\newline
%
\software{\texttt{numpy}~\citep{walt_numpy_2011}, 
\texttt{scipy}~\citep{jones_scipy_2001}, 
\texttt{matplotlib}~\citep{hunter_matplotlib_2007}, 
\texttt{pandas}~\citep{mckinney-proc-scipy-2010}
}
}

@@

This appendix derives Equation~\ref{eq:general_Gamma_a} through a more
straight-forward, but also more tedious, procedure than that of
Section~\ref{sec:general_formula}.   First, note that analogous to
Equation~\ref{eq:occ_rate_simple}, the apparent rate density $\Gamma\a$ can be
written
\begin{equation}
    \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
    \cdot \frac{1}{p_{\rm tra}(M\a)},
\label{eq:apparent_rate_density}
\end{equation}
where $n_{\rm det}$ is the number of detected planets, per unit
$(r\a, M\a)$, with apparent radius $r\a$ orbiting stars of
apparent mass $M\a$.   The planets with $(r\a, M\a)$ are associated
with systems of many different planetary and stellar properties, so
$n_{\rm det}(r\a, M\a)$ is given by the convolution of the true rate
density, $\Gamma(r, M)$, and $\mathcal{N}_\star(r\a, M\a; r, M)$, the
number of searchable stars per unit $(r\a, M\a)$ that give $(r\a,
M\a)$  when the true system actually has properties $(r, M)$.
Mathematically,
\begin{align}
    n_{\rm det}(r\a, M\a) &=
    \sum_i n_{\rm det}^i(r\a, M\a) \\
    &=
    \sum_i \int \mathrm{d}r \mathrm{d}M \,
    \mathcal{N}_\star^i(r\a,M\a; r,M)
    \cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
    \label{eq:n_det}
\end{align}
where $i$ specifies the type of true host star (0: single, 1:
primary, 2: secondary).  The problem reduces to the evaluation of
\begin{equation}
    \mathcal{N}_\star^i(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and
secondaries in binaries.

\paragraph{Single stars} For $i=0$, 
\begin{equation}
    \mathcal{N}_\star^0(r\a,M\a; r,M)
    =\hat{\delta}(r\a-r)\hat{\delta}(M\a-M) N_\star^0(r,M),
\end{equation}
where $\hat{\delta}$ is the Dirac delta function, so
\begin{equation}
    n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\cdot \Gamma_0(r\a, 
    M\a) \cdot p_{\rm tra}(r\a, M\a).
\end{equation}

\paragraph{Primaries in binaries}
The number of primaries with apparent parameters $(r\a,M\a)$ given the
true parameters $(r,M)$ is
\begin{equation}
    \mathcal{N}_\star^1(r\a, M\a; r, M)
    = \int 
      \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
    \label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the volume-limited binary mass ratio distribution.
Since we assume that binaries are assigned the mass of the primary,
\begin{equation}
    \mathcal{N}_{{\rm s},q}^1(r\a, M\a, q; r, M)
    \propto
    \hat{\delta}(M\a-M).
\end{equation}
In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at
$r\a=R\a\sqrt{\delta}$, and the observed depth is
\begin{equation}
    \delta
    = \left[{r\over R(M\a)}\right]^2\cdot {L(M\a) \over L_{\rm tot}(M\a, q)}
    \equiv \left[{r\over R(M\a)}\right]^2\cdot 
    \frac{1}{\mathcal{D}_1^2}
    \label{eq:delta_obs_primaries} 
\end{equation}
where
\begin{equation}
    \mathcal{D}_1=\sqrt{L_{\rm tot}(M\a, q) \over L(M\a)}.
\end{equation}
The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the
number of binaries that are searchable for a signal $\delta$
and that have mass ratio $q$:
\begin{equation}
    N_\star^0(r\a, M\a)\cdot
    {n\b\over n\s}\left[L_{\rm tot}(M\a, q) \over L(M\a)\right]^{3/2}.
    \label{eq:primary_normalization}
\end{equation}
where the argument for the number of searchable single stars,
$N_\star^0$, could also be expressed as $(\delta, L(M\a))$.
Applying Equation~\ref{eq:primary_normalization},
\begin{align}
    \mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M)
    &=N_\star^0(r\a, M\a)
    \cdot {n\b\over n\s} \cdot \mathcal{D}_1^3
    \cdot\hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_1}\right]\hat{\delta}(M\a-M).
    \label{eq:N_s_1}
\end{align}

\paragraph{Secondaries in binaries}
In this case, $M=qM_1=qM\a$, so
\begin{equation}
    \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
    \propto \hat{\delta}\left(M\a-{M\over q}\right).
    \label{eq:fancyN_s_2_prop}
\end{equation}
Again $\mathcal{N}_\star^2$ is non-zero only at
$r\a=R\a\sqrt{\delta}$, but this time
\begin{equation}
      \delta =
      \left[{r\over R(qM\a)}\right]^2 \cdot
      {L(qM\a) \over L_{\rm tot}(M\a, q)}
      \equiv
      \left[{r\over R(M\a)}\right]^2\cdot
      \frac{1}{\mathcal{D}_2^2},
\end{equation}
where
\begin{equation}
  \mathcal{D}_2
  =
  \frac{R(qM\a)}{R(M\a)}
  \sqrt{ \frac{L_{\rm tot}(M\a,q)}{L(qM\a)} }.
\end{equation}
The normalization remains the same as the previous case~--~we are
counting the searchable stars at a given observed depth $\delta$, and
the total luminosity of the binary is the same.  Thus,
\begin{equation}
    \mathcal{N}_\star^2(r\a, M\a; r, M)
    =\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r\a, M\a, q; r, M),
\end{equation}
where
\begin{align}
    \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
    =N_\star^0(r\a, M\a) \cdot \frac{n\b}{n\s} 
    \cdot \mathcal{D}_1^3
    \cdot \hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_2}\right]
    \hat{\delta} \left(M\a-{M\over q}\right).
    \label{eq:mathcal_N_s_2}
\end{align}

>>>>

\shortauthors{Bouma, Masuda, Winn}
\shorttitle{Binarity's Biases}

@@

\title{ Binarity's Biases on Transit Survey Occurrence Rates }
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author[0000-0002-0514-5538]{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author[0000-0003-1298-9699]{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author[0000-0002-4265-047X]{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%

@@

The astronomers analyze their data assuming that all stars are
single.  In particular they do not have accurate enough parallaxes to
tell that some of the stars are apparently overluminous.  They want to
compute the number of planets with size $r$ per star of mass $M$.  If
the total number of stars for which such planets could be detected
($N_\star$) and the number of detected planets ($N_{\rm det}$) are
both large, then the astronomers' estimate for the occurrence rate
($\Lambda$) is simply
\begin{equation}
  \Lambda = \frac{N_{\rm det}}{N_\star}
                    \, \frac{1}{p_{\rm tra}},
\label{eq:occ_rate_simple}
\end{equation}
where the geometric transit probability, $p_{\rm tra}$, accounts for
the fact that most planetary orbits are not aligned close enough with
our line of sight to produce transits.

@@

To calculate the occurrence rate of each planet type, our observers
identify the ``stars'' from their survey that appear to have been
searched for signals of each depth.  These transits are detected
within a certain maximum
distance~\citep[see][]{pepper_using_2003,pepper_searching_2005}, which
from Equation~\ref{eq:S_N_thresh} scales as
\begin{equation}
  d_{\rm max} \propto \delta \, L_{\rm tot}^{1/2}.
  \label{eq:dmax}
\end{equation}
Assuming that stars are uniformly distributed in space, the number of
searchable stars $N_\star$ is proportional to
\begin{equation}
    N_\star \propto n \delta^3 L_{\rm tot}^{3/2},
\label{eq:N_searchable_prop}
\end{equation}
where $n$ is the number per unit volume of single or binary star
systems.

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Apparent occurrence rate $\Lambda\a$, and occurrence rate $\Lambda$, 
        for a model with one type of star, one
        type of planet, and twin binaries (same as
        Figure~\ref{fig:model_1_volumes}).  We assume a twin binary
        fraction of $0.05$, and that single, primary, and secondary
        stars host planets at equal rates.  If the true planet radius
        is $r\p$, all planets detected in binaries will have apparent
        radii $r\a = r\p/\sqrt{2}$; Equation~\ref{eq:ratios} gives the
        normalizations.
    }
    \label{fig:occ_rate_model_1}
\end{figure}

@@

Suppose the occurrence rate densities for planets around
single stars, primaries, and secondaries are $\Gamma_0(r),
\Gamma_1(r)$, and $\Gamma_2(r)$, respectively. For a single planet
size,
\begin{equation}
    \Gamma_i(r) = \Lambda(r\p) \, \hat{\delta}(r-r\p),~~{\rm for}
    \ i\in\{0,1,2\},
    \label{eq:one_planet}
\end{equation} 
where $\hat{\delta}$ is the Dirac delta function.
The number of planets detected from singles, primaries, and
secondaries are then
\begin{align}
  n_{\rm det}^0(r\a)\mathrm{d}r\a &= 
      \frac{N_\star(r\a)}{1+\mu} p_{\rm tra}
      \Gamma_0(r\a)\mathrm{d}r\a,
  \label{eq:n0} \\
  n_{\rm det}^1(r\a)\mathrm{d}r\a &= 
      \frac{\mu N_\star(r\a)}{1+\mu} p_{\rm tra}
      \Gamma_1(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n1} \\
  n_{\rm det}^2(r\a)\mathrm{d}r\a &=
      \frac{\mu N_\star(r\a)}{1+\mu} p_{\rm tra}
      \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n2}
\end{align}
where $n_{\rm det}^i$ is the number of detections per unit apparent
radius for each respective type of star.

@@

We want an equation for $\Gamma\a(r\a,M\a)$, the apparent rate density
at each apparent planet radius and apparent stellar mass\footnote{By
assumption, the apparent stellar mass for single star systems is the
true mass. For binary systems, the apparent mass is the mass of the
primary.}.
Similar to Equation~\ref{eq:rate_density_defn}, we define
$\Gamma(r,M)$ as the number of planets per star, per unit planet radius,
per unit stellar mass.  Due to the varying binary mass ratios, we need
the following modifications to Equation~\ref{eq:formula_twin_binary}:
%
\begin{enumerate}
%
\item The Malmquist bias is different. The ratio between the number of
binary and single systems for which a transit of depth $\delta$ is
detectable, $\mu$, has changed.  At any $(r\a,M\a)$ pair, the number
of binary systems in the searchable volume with mass ratio $(q,
q+\mathrm{d}q)$ is now
\begin{equation}
    {N_\star(r\a)\over{1+\mu}} \, {n_{\rm b}\over n_{\rm s}}
    \left[{L_{\rm tot}(M\a, q) \over L(M\a)}\right]^{3/2}
    f(q)\,\mathrm{d}q,
    \label{eq:N_binaries}
\end{equation}
where $\mu$ is given by
\begin{equation}
    \mu= 
    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L_{\rm tot}(M\a, q)
    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
Binaries with larger mass ratios are overrepresented by a factor of
$\left[{L_{\rm tot}(M\a, q)/L(M\a)}\right]^{3/2}$ because the
sample of searchable binaries is magnitude-limited.  To obtain
the number of binary systems searched at each $(r\a,M\a)$ pair,
Equation~\ref{eq:N_binaries} needs to be integrated over $q$.  It
can then replace ${\mu N_\star(r\a)/(1+\mu)}$ in
Equations~\ref{eq:n1} and~\ref{eq:n2}.

@@

Taking these modifications into account, a general formula for the
apparent rate density follows:
\begin{align}
    \notag
    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu}
    \left\{ \Gamma_0(r\a, M\a)+ 
    \frac{n\b}{n\s}
    \left[ \int_0^1 \mathrm{d}q \,
           \mathcal{D}_1^3 f(q)\cdot
           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a)\,
    \right.   
    \right. \\
    & \quad\quad\quad\quad\quad \left.\left.
    +\int_0^1 {\rm d}q\, 
         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
         \frac{R(qM\a)}{R(M\a)} q^{-1/3}
    \right] \right\}.
    \label{eq:general_Gamma_a}
\end{align}
We give an alternative derivation in the
\hyperref[sec:appendix]{Appendix}.
With the definition of $\mu$ in Equation~\ref{eq:mu_general},
Equation~\ref{eq:general_Gamma_a} can also be expressed as
\begin{align}
    \notag
    \notag
    \Gamma\a(r\a,M\a)
    &= 
    {1\over 1+\mu}
    \left[
       \Gamma_0(r\a, M\a) \phantom{\frac{1}{1}}
       \right.&\\
       &\quad\quad \left.+\mu
       \left\langle
       \mathcal{D}_1\Gamma_1\left(\mathcal{D}_1r\a, M\a\right)
       +
       {q \mathcal{D}_2}\Gamma_2\left(\mathcal{D}_2r\a,
       qM\a\right) \cdot {R(qM\a) \over R(M\a)}q^{-1/3}
       \right\rangle
    \right],
\end{align}
where the angle brackets denote averaging over $\mathcal{D}_1^3f(q)$.
Summarized, the apparent rate density is a weighted sum of the rate
densities from singles, primaries, and secondaries.  The weights are
determined by the fraction $\mu$ and mass ratio distribution
$\mathcal{D}_1^3f(q)$ of binaries {\it in the searchable volume}.  The
fraction $\mu$ gives the relative contributions from singles and
binaries, and $\mathcal{D}_1^3 f(q)$ applies a Malmquist bias for
binaries that are brighter.  A final correction for secondaries
accounts for the overestimated transit probability.

@@

The rate density now varies not only with planet radius, but also
host star mass.  We can absorb this dependence into a power law,
\begin{equation}
    \Gamma_i(r,M) = Z_i \, \frac{r^\gamma}{\mathcal{N}_r} \,
    \frac{M^\zeta}{\mathcal{N}_M},
\end{equation}
where $Z_i$ is dimensionless, and the normalization constants carry
the units.% (each side has units $[r^{-1} M^{-1}]$).

@@

\begin{figure}[!t]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
    \caption{
        {\it Left:} apparent rate density ($\Gamma\a$) and rate density for 
        single stars ($\Gamma_0$). {\it Right:} apparent occurrence
        rate ($\Lambda\a$) and single star occurrence rate
        ($\Lambda_0$), over $0.5r_\oplus$ bins.  The true planet
        radius distribution is specified by
        Equation~\ref{eq:model3_radius_distribution}.  This model
        assumes that the observer knows the true properties of all the
        singles and primaries, and that the volume-limited mass ratios
        of secondaries are drawn from a uniform distribution. Further,
        we take $Z_0=Z_1=0.5$ throughout; $Z_0,Z_1,Z_2$ are the number
        of planets per single, primary, and secondary star.  The rate
        and rate density are related by $\Lambda|_a^b =
        \int_{a}^{b}\Gamma\,{\rm d}r$.
    }
    \label{fig:occ_rate_model_3_log}
\end{figure}

@@

\acknowledgements{
It was a pleasure discussing this study with T.~Barclay, W.~Bhatti,
J.~Christiansen, F.~Dai, and T.~Morton.  This work made use of NASA's
Astrophysics Data System Bibliographic Services.
%
\newline
%
\software{\texttt{numpy}~\citep{walt_numpy_2011}, 
\texttt{scipy}~\citep{jones_scipy_2001}, 
\texttt{matplotlib}~\citep{hunter_matplotlib_2007}, 
\texttt{pandas}~\citep{mckinney-proc-scipy-2010},
\texttt{IPython}~\citep{perez_2007}
}
}

@@

This appendix derives Equation~\ref{eq:general_Gamma_a} through a more
straight-forward, but also more tedious, procedure than that of
Section~\ref{sec:general_formula}.   First, note that analogous to
Equation~\ref{eq:occ_rate_simple}, the apparent rate density $\Gamma\a$ can be
written
\begin{equation}
    \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
    \, \frac{1}{p_{\rm tra}(M\a)},
\label{eq:apparent_rate_density}
\end{equation}
where $n_{\rm det}$ is the number of detected planets, per unit
$(r\a, M\a)$, with apparent radius $r\a$ orbiting stars of
apparent mass $M\a$.   The planets with $(r\a, M\a)$ are associated
with systems of many different planetary and stellar properties, so
$n_{\rm det}(r\a, M\a)$ is given by the convolution of the true rate
density, $\Gamma(r, M)$, and $\mathcal{N}_\star(r\a, M\a; r, M)$, the
number of searchable stars per unit $(r\a, M\a)$ that give $(r\a,
M\a)$  when the true system actually has properties $(r, M)$.
Mathematically,
\begin{align}
    n_{\rm det}(r\a, M\a) &=
    \sum_i n_{\rm det}^i(r\a, M\a) \\
    &=
    \sum_i \int \mathrm{d}r \mathrm{d}M \,
    \mathcal{N}_\star^i(r\a,M\a; r,M)
    \, \Gamma_i(r,M) \, p_{\rm tra}(r,M),
    \label{eq:n_det}
\end{align}
where $i$ specifies the type of true host star (0: single, 1:
primary, 2: secondary).  The problem reduces to the evaluation of
\begin{equation}
    \mathcal{N}_\star^i(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and
secondaries in binaries.

\paragraph{Single stars} For $i=0$, 
\begin{equation}
    \mathcal{N}_\star^0(r\a,M\a; r,M)
    =\hat{\delta}(r\a-r)\hat{\delta}(M\a-M) N_\star^0(r,M),
\end{equation}
where $\hat{\delta}$ is the Dirac delta function, so
\begin{equation}
    n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\, \Gamma_0(r\a, 
    M\a) \, p_{\rm tra}(r\a, M\a).
\end{equation}

\paragraph{Primaries in binaries}
The number of primaries with apparent parameters $(r\a,M\a)$ given the
true parameters $(r,M)$ is
\begin{equation}
    \mathcal{N}_\star^1(r\a, M\a; r, M)
    = \int 
      \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
    \label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the volume-limited binary mass ratio distribution.
Since we assume that binaries are assigned the mass of the primary,
\begin{equation}
    \mathcal{N}_{{\rm s},q}^1(r\a, M\a, q; r, M)
    \propto
    \hat{\delta}(M\a-M).
\end{equation}
In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at
$r\a=R\a\sqrt{\delta}$, and the observed depth is
\begin{equation}
    \delta
    = \left[{r\over R(M\a)}\right]^2\, {L(M\a) \over L_{\rm tot}(M\a, q)}
    \equiv \left[{r\over R(M\a)}\right]^2\, 
    \frac{1}{\mathcal{D}_1^2}
    \label{eq:delta_obs_primaries} 
\end{equation}
where
\begin{equation}
    \mathcal{D}_1=\sqrt{L_{\rm tot}(M\a, q) \over L(M\a)}.
\end{equation}
The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the
number of binaries that are searchable for a signal $\delta$
and that have mass ratio $q$:
\begin{equation}
    N_\star^0(r\a, M\a)\,
    {n\b\over n\s}\left[L_{\rm tot}(M\a, q) \over L(M\a)\right]^{3/2}.
    \label{eq:primary_normalization}
\end{equation}
where the argument for the number of searchable single stars,
$N_\star^0$, could also be expressed as $(\delta, L(M\a))$.
Applying Equation~\ref{eq:primary_normalization},
\begin{align}
    \mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M)
    &=N_\star^0(r\a, M\a)
    \, {n\b\over n\s} \, \mathcal{D}_1^3
    \,\hat{\delta} \left(r\a-\frac{r}{\mathcal{D}_1}\right)\hat{\delta}(M\a-M).
    \label{eq:N_s_1}
\end{align}

\paragraph{Secondaries in binaries}
In this case, $M=qM_1=qM\a$, so
\begin{equation}
    \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
    \propto \hat{\delta}\left(M\a-{M\over q}\right).
    \label{eq:fancyN_s_2_prop}
\end{equation}
Again $\mathcal{N}_\star^2$ is non-zero only at
$r\a=R\a\sqrt{\delta}$, but this time
\begin{equation}
      \delta =
      \left[{r\over R(qM\a)}\right]^2 \,
      {L(qM\a) \over L_{\rm tot}(M\a, q)}
      \equiv
      \left[{r\over R(M\a)}\right]^2\,
      \frac{1}{\mathcal{D}_2^2},
\end{equation}
where
\begin{equation}
  \mathcal{D}_2
  =
  \frac{R(qM\a)}{R(M\a)}
  \sqrt{ \frac{L_{\rm tot}(M\a,q)}{L(qM\a)} }.
\end{equation}
The normalization remains the same as the previous case~--~we are
counting the searchable stars at a given observed depth $\delta$, and
the total luminosity of the binary is the same.  Thus,
\begin{equation}
    \mathcal{N}_\star^2(r\a, M\a; r, M)
    =\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r\a, M\a, q; r, M),
\end{equation}
where
\begin{align}
    \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
    =N_\star^0(r\a, M\a) \, \frac{n\b}{n\s} 
    \, \mathcal{D}_1^3
    \, \hat{\delta} \left(r\a-\frac{r}{\mathcal{D}_2}\right)
    \hat{\delta} \left(M\a-{M\over q}\right).
    \label{eq:mathcal_N_s_2}
\end{align}
